Electricity Usage in Toronto’s Public Facilities: Analyzing the Impact of Building Size on Energy Consumption

### 2024-09-24 paper/paper.qmd
changed

>>>>

Public infrastructure, including schools, libraries, healthcare centers, and government offices, forms the backbone of urban services in any modern city. As Toronto continues to expand, managing electricity usage in public buildings becomes increasingly critical. Energy efficiency in public facilities not only reduces operational costs but also contributes to environmental goals, such as carbon reduction and climate change mitigation \cite{droege2018urban}.
